Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-05-06 paper.tex
Categorized content to be placed in methods section into subsections
more flesh to paper

In small angle approximation, any length $R = D_L \theta$.

@@

@@

\subsection{Modelling of Foreground Lens and Background Galaxies}

\begin{enumerate}
    \item Calculate tangential shear and deflection angle for NFW and cored isothermal profiles.
    \item Consider single foreground lens halo with many background galaxies.
    \begin{itemize}
        \item Start with one NFW halo, then maybe consider more tests.
    \end{itemize}
    \item Construct background galaxies:
    \begin{itemize}
        \item Number density on sky: 50 galaxies/square arcminute
        \item Intrinsic ellipticity drawn from Gaussian distribution with $\mu=0, \sigma=0.2$
        \item Assume they are all that the same distance $D_S$ since this can be determined by redshift (neglecting some noise)
    \end{itemize}
    \item Recommended values:
    \begin{itemize}
        \item $z_L = 0.3$
        \item $z_S = 1.0$
        \item $M_{halo} = 10^{15} M_\odot$
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies, get fake data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
    \item Bin galaxies in annuli by $\theta$ value (use log bins for theta)
    \item Calculate mean and standard deviation of ellipticity
    \item Attempt to fit both NFW and isothermal profiles, see if the fit is distinguishable
\end{enumerate}

@@

\section{Results}

>>>>

At small angles, we can assume from small angle approximations that $R = D_L \theta$.

@@

The isothermal sphere profile is commonly used thanks to the convenience in simplifications.

@@

\subsection{Modelling of Foreground Lens and Background Galaxies}
\begin{enumerate}
    \item Consider single foreground lens halo with many background galaxies.
    \begin{itemize}
        \item Start with one NFW halo, then maybe consider more tests.
    \end{itemize}
    \item Construct background galaxies:
    \begin{itemize}
        \item Number density on sky: 50 galaxies/square arcminute
        \item Intrinsic ellipticity drawn from Gaussian distribution with $\mu=0, \sigma=0.2$
        \item Assume they are all that the same distance $D_S$ since this can be determined by redshift (neglecting some noise)
    \end{itemize}
    \item Recommended values:
    \begin{itemize}
        \item $z_L = 0.3$
        \item $z_S = 1.0$
        \item $M_{halo} = 10^{15} M_\odot$
    \end{itemize}
\end{enumerate}

\subsection{Generating Simulated Data}
\begin{enumerate}
\item Apply shear and deflection angle to background galaxies, get simulated data: $N$ sets of $\epsilon_1$, $\epsilon_2$, $\theta_1$, $\theta_2$
\end{enumerate}

\subsection{Data Analysis and Density Profile Determination}
\begin{enumerate}
\item Bin galaxies in annuli by $\theta$ value (use log bins for theta)
\item Calculate mean and standard deviation of ellipticity
\item Attempt to fit both NFW and isothermal profiles, see if the fit is distinguishable
\end{enumerate}

@@

\section{Results and Conclusion}

From our data analysis, we were able to find the more probable density profile of a simulated data set.
Future goals include the use of these methods to analyze observed data of galaxy clusters to find the density profile of their lenses.
